Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex
re-export the figure in different proportions
back down to 8 pages

%%Figure 1. HRPPC component relationships and data flow
\begin{figure}
\begin{center}
 \includegraphics[width=12cm,keepaspectratio=true]{plantscan-workflow-figure1.png}
 % plantscan-workflow-figure1.png: 598x330 pixel, 72dpi, 21.10x11.64 cm, bb=0 0
%598 330

@@

DAP is the visible part of the system. Other than standard web servers,
databases and application servers, additional required server-side
infrastructure includes petabyte-level, multi-decade, backed-up disk storage,
integrity checking, and automated migration of data collections to and from tape
storage.

>>>>

%%Figure 1. HRPPC component relationships and data flow
\begin{figure}
\begin{center}
 \includegraphics[width=11.5cm,keepaspectratio=true]{podd-workflow-figure1.png}
 % plantscan-workflow-figure1.png: 598x330 pixel, 72dpi, 21.10x11.64 cm, bb=0 0
%598 330

@@

%DAP is the visible part of the system. Other than standard web servers,
%databases and application servers, additional required server-side
%infrastructure includes petabyte-level, multi-decade, backed-up disk storage,
%integrity checking, and automated migration of data collections to and from tape
%storage.
